\Large \bf Rethinking Service Systems: \\ A Path Towards Secure and Equitable Resource Markets

### 2020-06-04 CESC-submission/paper.tex
Edits & suggestions

\begin{abstract}
Escalating demand for digital services has motivated building non-traditional solutions to reduce costs and achieve a greater level of flexibility. Among these solutions, peer-assisted models are gaining more popularity in replacing infrastructure-based (possibly) centralized approaches. Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to reward for the service, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system. We present a generic framework for building distributed service markets by utilizing these new technologies. We also discuss the security and efficiency challenges, with a focus on how the economic aspects impact system design and threat mitigation, and conclude with some potential solutions.
\end{abstract}

@@

These issues motivated the community to revisit old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others. In order to encourage the collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources. This paradigm builds flexible systems, where anyone can start or stop the service at any time. It also scales more easily with demand and extends the network coverage because peers from anywhere can join. Furthermore, this paradigm builds transparent and equitable ecosystems in which participants can negotiate service terms and price directly instead of having a few entities monopolizing the market.

@@

However, the open access environment of P2P networks (i.e., allowing anyone to join and dealing with untrusted participants) introduces several security and performance challenges that need to be addressed before having any practical deployment. In addition, having monetary incentives motivates attackers to attack the system in novel ways to maximize their financial profits. Thus, traditional practices of secure systems design need to be modified and adapted to account for such factors.

@@

The best practice for designing a secure system requires a threat modeling step to investigate potential security risks. Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system. For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion.

@@

It should be noted that the threat modeling step need to be revisited each time the system design is altered. Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.  \\

\noindent{\bf Unique Aspects of Operating a Distributed Market.} The open access work environment helps to create flexible services and transparent ecosystems. However, this comes at a cost. Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay servers - before or after providing the service? If paid first, a malicious server may not serve the customer, and if served first, a malicious customer may not pay afterwards.

Furthermore, accounting attacks, in which participants collude with each other pretending that the service has been delivered, could be a hammer that may destroy the market. This is a particular problem in systems that require sponsoring service requests. For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service. In this case, caches (or servers in general) and clients may collude so that clients pretend to be served, allowing servers to collect payments from the sponsor for free.

The above security issues (an many others depending on the service type) require a careful design of a decentralized service-payment exchange protocol that can reduce the risks of dealing with untrusted, possibly colluding parties. Such a protocol represents the backbone of the resource market; if it fails the whole market fails. Servers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive. Operating the market also requires devising mechanisms for service pricing, term negotiation for server recruiting, and matching protocols to match these servers with interested customers. \\

\noindent{\bf Financial and Cryptographic Security Measures.} Usually, security threats are mitigated by using cryptographic means (e.g., encryption and digital signatures), or algorithmic approaches (e.g., ordering the actions in a way that enforces secure behavior). Monetary-incentivized systems introduce new types of attacks that cannot be addressed using conventional approaches. In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means. These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock a penalty deposit that is forfeited if he/she is caught cheating. Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly. And third, designing service pricing policies that make it more profitable on the long run to act honestly in every service request than cheating (even if cheating is not detected). Such techniques make cheating unprofitable so that rational parties will choose to follow the protocol.

For example, to reduce the risks of the impossibility of fair exchange, micropayments can be employed. That is, instead of paying a large chunk of money for the full service, the payment is divided into small values, each of which is exchanged for a small service amount. For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once. Hence, a server loses a small payment if a client does not pay after receiving a chunk. Similarly, a client loses a small payment if it pays in advance and the server does not send a data chunk in return.

On the other hand, to thwart accounting attacks, system designers need to incorporate suitable techniques to prove or confirm resource expenditure, and consequently, confirm that payments are well deserved. In online content delivery, for example, the CAPnet puzzle~\cite{Almashaqbeh19b} can be used to ensure that caches have delivered the requested content. The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content. In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a server is still storing the clients’ files with the agreed-upon number of replicas. Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a server pledged when joining the system~\cite{filecoin}. Thus, the type of the provided service directly influences the delivery confirmation mechanism that need to be deployed. \\

\noindent{\bf Optimize for Efficiency.} Although designing a secure system is the ultimate goal, efficiency is an important driving factor of practical adoption and deployment. System designers need to exploit any opportunity that allows for optimizing performance. This also involves choosing the right trade-off between security and efficiency in the sense of risk management. That is, threats that have high impact need to be prioritized over low impact ones. Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective venue to utilize.

Furthermore, reducing interaction between participants is beneficial. It speeds up the service and promotes the system’s scalability. This can take the form of batching requests/replies between customers and servers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.

@@

\section{Impact of Financial Incentives on Service Delivery}
\vspace{-4pt}
In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery. We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the servers. In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming servers' activity. We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impact the financial motivations of attackers. Such an issue is a great example of how cryptocurrency-based services introduce new economic aspects that may evolve over time, which need to be reflected on the system design. \\

\noindent{\bf An overview of the NuCypher network.} The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the ciphertext without revealing anything about the
decryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the service load an Ursula
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, if she cheats and this cheating is detected.

@@

\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is inflation rewards, i.e., newly minted NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage adoption. It is expected that these rewards will disappear as the token cap is reached, similar to other cryptocurrencies in the space.

Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round. Confirming the status of being online is done by calling a 
simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online. Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.

Although this approach of rewards computation and activity monitoring was enough to reach a MVP, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation (both fees and inflation) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or amalicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service. Ursula can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activityfunction. This allows Ursula to collect both inflation rewards and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
\end{itemize}

Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity. Then we need to adapt the reward computation accordingly to factor in the amount of delivered service. These are introduced in the rest of this section. \\

\noindent{\bf Problem definition based on network operation stage.} The confirm activity problem is defined differently based on the stage of the network operation. In early network launch, when inflation rewards are 
still distributed, we are concerned with the availability of Ursulas and being willing to 
serve all requests coming from Bob. In other words, regardless of the number of requests served, the rewards value (both inflation and fees) will be computed based on the period during which Ursula 
is online and well-behaving. While in later stages, when inflation rewards disappear 
and only fees exist, confirm activity will be tied to providing the re-encryption 
service in the sense that the payment will be computed based on the amount of 
service provided. This requires Ursula to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a given period. To make the distinction 
clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
service activity}. \\

\noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem. These solutions differ in the trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows. Before that, we review the adopted threat model.

@@

However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically efficient, and hence, not an issue in our system. The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal. This means that colluding with Bob will save minimal resources, which makes this collusion case unappealing to rational Ursulas. This case is a great example of how traditional threat modeling and risk management practices differ from those economic-oriented ones in ruling out financially-inefficient threats.

@@

\paragraph{Confirm availability solution.} Here we use a detect-and-punish approach embedded within an optimistic service monitoring process. This means that it is only invoked when Bob complains that an Ursula is unresponsiveness. In detail, for each round\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process. Then map each hash to an Ursula index as found in the list of working Ursulas recorded on the blockchain within the StakeEscrow smart contract of NuCypher. This process is repeated until a set of distinct Ursulas is selected. Note that anyone can perform this process and verify its outcome.} Bob proceeds as usual by contacting the list of working Ursulas received from Alice for the re-encryption service. If a working Ursula does not reply, Bob complains to a gateway Ursula and hands her the request. This gateway mediates the service process in order to check if Bob's claim is valid. In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer. If one is received, the gateway forwards it to Bob and closes the complain.

On the other hand, meaning no response is received, the gateway notifies the rest of gateways selected for that round to repeat the same process. If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract. At that time, a part of the working Ursula stake is slashed (with a value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment. This punishment makes cheating unprofitable, and hence, unappealing to rational working Ursulas. A detailed technical version of this solution is available in~\cite{confirm-activity-draft}.

As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both inflation rewards and service fees in proportion to her availability period and the number of policies she holds. In other words, reward computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.

@@

As for the \emph{ZKP-based} solution, recall that in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}. We can combine the proofs of all served requests within a round into one attesting to the following statement: "An Ursula has served $\omega$ distinct requests correctly" for some positive integer $\omega$ representing the number of served requests. This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.

@@

>>>>

\begin{abstract}
Escalating demand for digital services has motivated building non-traditional solutions to reduce costs and achieve a greater level of flexibility. Among these solutions, peer-assisted models are gaining more popularity in replacing infrastructure-based (possibly) centralized approaches. Cryptocurrencies have strengthened this trend by providing a fully distributed mechanism to compensate service provision, and their blockchains and consensus protocols offer a trustless and publicly verifiable way to govern the system. We present a generic framework for building distributed service markets by utilizing these new technologies. We also discuss the security and efficiency challenges, with a focus on how the economic considerations impact system design and threat mitigation, and conclude with some potential solutions.
\end{abstract}

@@

These issues motivated the community to revisit old ideas of peer-to-peer (P2P) based models in which anyone is allowed to join the system and serve others. In order to encourage the collaborative work and compliance with the protocol, payments are provided in return, which creates a market for trading resources. This paradigm builds flexible systems, where customers can start or stop the service at any time. It also scales more easily with demand and extends the network coverage because peers from anywhere can join. Furthermore, this paradigm builds transparent and equitable ecosystems in which participants can negotiate service terms and price directly instead of having a few entities monopolizing the market.

@@

However, the open access environment of P2P networks (i.e., allowing anyone to join and dealing with untrusted participants) introduces several security and performance challenges that need to be addressed before having any practical deployment. In addition, having monetary incentives motivates attackers to attack the system in novel ways to maximize their financial profits. Thus, traditional practices of secure systems design need to be modified and expanded to account for such factors.

@@

The best practice for designing a secure system requires a threat modeling step to investigate potential security risks. Such a model can guide designers in deploying the proper countermeasures, and evaluating the security level of a system. For resource markets, building a threat model requires a framework that can handle large-scale distributed systems, explicitly account for the financial motivations of the attackers, and help in spotting any potential collusion or sybil attack.

@@

It should be noted that the threat modeling steps need to be revisited each time the system design is altered. Furthermore, it should be performed as the last step before shipping the system to argue formally about its security.  \\

\noindent{\bf Unique Aspects of Operating a Distributed Market.} The open access work environment helps to create flexible services and transparent ecosystems. However, this comes at a cost. Dealing with untrusted parties means that fair exchange is impossible~\cite{Even80,Pagnia99}, which raises the question of when to pay service-providers - before or after providing the service? If paid first, a malicious service-provider may not serve the customer, and if served first, a malicious customer may not pay afterwards.

Furthermore, accounting attacks, in which participants collude with each other pretending that the service has been delivered, could be a hammer that may destroy the market. This is a particular problem in systems that require sponsoring service requests. For example, in content distribution, a publisher (e.g., Netflix) can hire caches to distribute content to its clients, and hence, it pays for the service. In this case, caches (or service-providers in general) and clients may collude so that clients pretend to be served, allowing service-providers to collect payments from the sponsor for free.

The above security issues (an many others depending on the service type) require a careful design of a decentralized service-payment exchange protocol that can reduce the risks of dealing with untrusted, possibly colluding parties. Such a protocol represents the backbone of the resource market; if it fails the whole market fails. Service-providers will not be willing to participate if they are not being paid, and same for customers, they will not be willing to use the system if they pay for a service that they do not receive. Operating the market also requires devising mechanisms for service pricing, term negotiation for service-provider recruiting, and matching protocols to match these service-providers with interested customers. \\

\noindent{\bf Financial and Cryptographic Security Measures.} Usually, security threats are mitigated by using cryptographic means (e.g., encryption and digital signatures), or algorithmic approaches (e.g., ordering the actions in a way that enforces secure behavior). Monetary-incentivized systems introduce new types of attacks that cannot be addressed using conventional approaches. In particular, having financially-motivated attackers introduces new threat vectors that need to be mitigated by using financial means. These fall into three categories: first, detect-and-punish mechanisms, where any participant is required to lock collateral that is forfeited if he/she is caught cheating. Second, designing algorithms that, if performed maliciously, require larger amounts of resources than when performed honestly. And third, designing service pricing and payments mechanisms that make it more profitable on the long run to act honestly in every service request than cheating or ignoring the request (even if cheating or ignoring are not detectable). Such techniques make cheating unprofitable so that the majority of rational parties will choose to follow the protocol.

For example, to reduce the risks of the impossibility of fair exchange, micropayments can be employed. That is, instead of paying a large chunk of money for the full service, the payment is divided into small values, each of which is exchanged for a small service amount. For instance, one can pay for retrieving a file in small data chunks instead of paying for the full retrieval all at once. Hence, a service-provider loses a small payment if a client does not pay after receiving a chunk. Similarly, a client loses a small payment if it pays in advance and the service-provider does not send a data chunk in return.

On the other hand, to thwart accounting attacks, system designers need to incorporate suitable techniques to prove or confirm resource expenditure, and consequently, confirm that payments are well deserved. In online content delivery, for example, the CAPnet puzzle~\cite{Almashaqbeh19b} can be used to ensure that caches have delivered the requested content. The design of this puzzle follows the second category mentioned above, where solving the puzzle without doing the work is more expensive (resources-wise) than solving it after retrieving the content. In file storage, proof-of-replication~\cite{Fisch19} can be used to prove that a service-provider is still storing the clients’ files with the agreed-upon number of replicas. Here, a detect-and-punish mechanism is used, where failing in providing a correct proof leads to slashing part of the deposit a service-provider pledged when joining the system~\cite{filecoin}. Thus, the type of the provided service directly influences the mechanisms for delivery confirmation, compensation and punishment that need to be deployed. \\

\noindent{\bf Optimize for Efficiency.} Although designing a secure system is the ultimate goal, efficiency is an important driving factor of practical adoption and deployment. System designers need to exploit any opportunity that allows for optimizing performance. This also involves choosing the right trade-off between security and efficiency in the sense of risk management. That is, threats that have high impact need to be prioritized over low impact ones. Moreover, looking into alternative cryptographic primitives that are lightweight, or optimize their implementation, while maintaining the required security guarantees is another effective avenue to utilize.

Furthermore, reducing interaction between participants is beneficial. It speeds up the service and promotes the system’s scalability. This can take the form of batching requests/replies between customers and service-providers to reduce costs and optimize resource allocation, in addition to batch or aggregate record verification on the blockchain.

@@

\section{Impact of Financial Incentives on Service Delivery}
\vspace{-4pt}
In this section, we elaborate on one of the important issues in distributed resource markets, namely, service delivery. We examine how financial incentives affect which technique to deploy in order to enforce the honest behavior of the service-providers. In particular, we report on some work we have done in the NuCypher network under the umbrella of confirming service-providers' activity. We show how early stages of network launch differ from later periods when the network is stable, particularly in terms of reward computation, which in turn impact the financial motivations of attackers. Such an issue is a great example of how cryptocurrency-based services introduce new economic aspects that may evolve over time, which need to be reflected on the system design. \\

\noindent{\bf An overview of the NuCypher network.} The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management
system, encryption, and access control service. It uses proxy re-encryption, namely, the
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted
documents through a public network. This network is composed of a set of semi-trusted
re-encryption service-providers, or Ursulas, that implement access control policies created by data
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the ciphertext without revealing anything about the
decryption keys or the raw data to the intermediate service-providers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the service load an Ursula
may receive. This stake is also used to punish Ursula financially, by forfeiting part
of it, if she cheats and this cheating is detected.

@@

\noindent{\bf Monetary incentives in the NuCypher network.} Ursulas are rewarded for the re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distribted on a schedule enforced by the NuCypher protocol. The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.

Currently, the subsidy size in each round or period are computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round. Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online. Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.

Although subsidy computation and collection based on activity monitoring is reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The revenue computation (both fees and subsidies) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service. Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function. This allows Ursula to collect both subsidies and fees without doing all (or even most) of the necessary work. Even worse, Ursula will be able to get her stake back once it unlocks.
\end{itemize}

Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's minute-to-minute availability and service activity. Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient. These are introduced in the rest of this section. \\

\noindent{\bf Problem definition based on network operation stage.} The confirm activity problem is defined differently based on the stage of the network operation. In the first 5 to 8 years after launch, when subsidy rewards are
still distributed, we are concerned with the availability of Ursulas and their willingness to
serve all requests coming from Bob. In other words, regardless of the number of requests served, the revenue total (both subsidies and fees) will be computed based on the length of time in which Ursula
is online and well-behaved. In later stages, when subsidies disappear
and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption
service, in the sense that the payment will be partially computed based on the amount of
service provided. This requires Ursula to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a given period. To make the distinction 
clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
service activity}. \\

\noindent{\bf Confirm availability and service activity solutions.} In~\cite{confirm-activity-draft}, we introduce several solutions for both forms of the above problem. These solutions differ with respect to trust, efficiency, interactivity, and resource requirements, in addition to their security guarantees, which we present briefly in what follows. Before that, we review the adopted threat model.

@@

However, we argue that collusion between Bob and Ursula to perform accounting attacks (i.e., Bob pretends that service has been delivered allowing Ursula to collect payments for free) is not economically advantageous, and hence, not an issue in our system. The reason is that the amount of work an Ursula does when replying to a re-encryption request is minimal. This means that colluding with Bob to fake re-encryptions will save minimal resources and has no clear economic gain (such as extra subsidies), which makes this collusion case unappealing to rational Ursulas. This case is a great example of how traditional threat modeling and risk management practices differ from those economic-oriented ones in ruling out financially-inefficient threats.

@@

\paragraph{Confirm availability solution.} Here we use a detect-and-punish approach embedded within an optimistic service monitoring process. This means that it is only invoked when Bob complains that an Ursula is unresponsive. In detail, for each round\footnote{A round is the time needed to mine a block or several blocks on the underlying blockchain.} a set of Ursulas is selected at random to act as gateways (or service watchers).\footnote{One approach to do that in a distributed way is to feed a random beacon (like block hashes in the random oracle model) to an iterative hashing process. Then map each hash to an Ursula index as found in the list of working Ursulas recorded on the blockchain within the StakeEscrow smart contract of NuCypher. This process is repeated until a set of distinct Ursulas is selected. Note that anyone can perform this process and verify its outcome.} Bob proceeds as usual by contacting the list of working Ursulas received from Alice for the re-encryption service. If a working Ursula does not reply, Bob complains to a gateway Ursula and hands her the request. This gateway mediates the service process in order to check if Bob's claim is valid. In other words, she challenges the working Ursula by forwarding the request again and waiting for an answer (which must arrive within a specified, universal time window). If one is received, the gateway forwards it to Bob and closes the complaint.

On the other hand, meaning no response is received, the gateway notifies the rest of gateways selected for that round to repeat the same process. If no response is received by any of them, the quorum signs a proof-of-unavailability (e.g., by using collective signing~\cite{syta2016keeping}) against the working Ursula stating that she is unavailable and submit this proof to the NuCypher staking contract. At that time, a part of the working Ursula stake is slashed (with a minimum value derived based on the additional utility gain an Ursula collects by faking to be online) as a punishment. This punishment makes cheating unprofitable, and hence, unappealing to rational working Ursulas. A detailed technical version of this solution is available in~\cite{confirm-activity-draft}.

As long as Ursula is behaving well and no valid complaints from Bob, this Ursula will collect both subsidies and service fees in proportion to her availability period and the number of policies she holds. In other words, revenue computation follows the same current approach outlined earlier since our concern is to encourage adoption especially when service demand is low at the beginning.

@@

As for the \emph{ZKP-based} solution, in the NuCypher network each Ursula produces a zero knowledge proof attesting to the correctness of the re-encryption she performed to be checked by Bob~\cite{umbral2018}. We can combine the proofs of all served requests within a round into one attesting to the following statement: "An Ursula has served $\omega$ distinct requests correctly" for some positive integer $\omega$ representing the number of served requests. This accumulation can be done by using generic techniques like proof carrying data (PCD)~\cite{chiesa2010proof} or incrementally verifiable computation (IVC)~\cite{valiant08}.

@@

Another issue is regarding the payment computation. During early stages when the network launches, we anticipate a limited adoption and service demand. Thus, we reward Ursulas for just being online to encourage adoption. While in later stages, payments will be dispensed partially in proportion to the actual amount of service requests an Ursula answers. This is due to the fact that later on the subsidies will effectively disappear, i.e., the majority of tokens in the network will be minted, and the service fees are the only source of income. To incentivize Ursula to provide a correct and timely service, these fees should be computed based on the actual amount of service. This shows how changes in incentive alignment lead to different views on how to distribute these incentives and ensure the security of the system.
